Taking Dyads Seriously

### 2018-03-05 paper/netsMatter.tex
getting closer
SM there are some issues you need to address, noted herein.  Let me know when you are finished, please.

\small{\singlespacing{
\begin{abstract}
	Much of international relations scholarship concerns dyads: dyadic hypotheses and especially dyadic data. Yet, modeling approaches that fail to properly capture the data generating process behind dyadic events will suffer from biased coefficients and poorly calibrated standard errors. We introduce a regression-based approach, the Additive and Multiplicative Effects (AME) model, that better accounts for the dependencies in dyadic data. First, we conduct a simulation to highlight how the model captures dependencies and show that accounting for these processes improves our ability to conduct inference. Second, we compare the AME model to approaches used in three studies from recent international relations scholarship. For each study, we find that the modeling approach used in the original study performs notably worse at capturing the data generating process compared to the AME. Further, conventional methods misstate the effect of key variables and the uncertainty in these effects. In sum, our work shows the consequences of failing to take the dependencies inherent to dyadic data seriously. Most importantly, by better modeling the data generating process underlying political phenomena, the AME framework improves scholars' ability to conduct inferential analyses. 
\end{abstract}
}}

@@

%\bibliography{/Users/maxgallop/documents/whistle/master}
%\bibliography{/Users/s7m/whistle/master}
 % \bibliography{/Users/mdw/Git/whistle/master}
 \bibliography{/Users/cassydorff/ProjectsGit/master}
% \bibliographystyle{authordate1}
\bibliographystyle{sm}
% \clearpage
% \section*{All About Us}

>>>>

\small{\singlespacing{
\begin{abstract}
	Much international relations scholarship concerns dyads. Dyadic hypotheses and especially dyadic data abound. Standard mnodeling approaches fail to adequately capture the data generating process behind dyadic events and processes. As a result, they suffer from biased coefficients and poorly calibrated standard errors. We introduce a regression-based approach, the Additive and Multiplicative Effects (AME) model, that better accounts for the inherent dependencies in dyadic data. First, we conduct a simulation to highlight how the model captures dependencies and show that accounting for these processes improves our ability to conduct inference about dyadic hypotheses. Second, we compare the AME model to approaches used in three prominent studies from recent international relations scholarship. For each study, we find that compared to AME, the modeling approach used in each original study performs notably worse at capturing the data generating process. Further, conventional methods misstate the effect of key variables and the uncertainty in these effects. Finally, AME dominates standard approaches in terms of out-of-sample fit. In sum, our work shows the consequences of failing to take the dependencies inherent to dyadic data seriously. Most importantly, by better modeling the data generating process underlying political phenomena, the AME framework improves scholars' ability to conduct inferential analyses. 
\end{abstract}
}}

@@

%\bibliography{/Users/maxgallop/documents/whistle/master}
%\bibliography{/Users/s7m/whistle/master}
 \bibliography{/Users/mdw/Git/whistle/master}
% \bibliography{/Users/cassydorff/ProjectsGit/master}
% \bibliographystyle{authordate1}
\bibliographystyle{sm}
% \clearpage
% \section*{All About Us}
